How has the Brazilian Amazon been constructed as a problem:presidential speeches and transnational politics since 1985

### 2022-12-09 Submission/draft/draft_resubmission.rmd
More updates to methods section

To analyze how presidents construct the Amazon as a problem, we build upon the dataset provided by (Cezar 2020) which contains all official speeches by Brazilian Presidents from 1985 to 2019 scrapped from the archives of the Brazilian Presidential Library. We update the dataset by scraping and adding all official speeches from 2020 and 2021. The final dataset encompasses 6130 speeches. Then, we proceed to identify speeches that refer to the Amazon as a region, people, or forest. We do so by detecting all speeches in which the stem “amazon” appears. In Portuguese, the stem captures terms such as “Amazonia”, “Amazonica”, “Amazonidas”, “Amazonense(s)”, “Amazonas”, among others. We find that 946 speeches are, at least partially, about the Amazon.

Using the poldis R package (Sposito 2021), we proceed to extract two sentences before and two sentences after the sentence in which the stem “amazon” appears. We opt for picking two sentences around, rather than words, because sentences usually contain a cohesive idea. When an Amazonian statement contains two or more matches of the stem “amazon”, we get two sentences before the first match and two sentences after the last match. By doing so we create our unit of analysis: an Amazonian statement. Amazonian statements represent text portions that are meaningful for our specific purpose. This process yields 2014 unique Amazonian statements about the Amazon. On average, an Amazonian statement contains 123 words.

Our approach to text coding is threefold. First, we follow the Amazonian historiography literature to develop a codebook to code Amazonian statements as one, or more, problem-constructions (see codebook in appendix). In their conceptualization, each problem-construction is mutually exclusive, meaning that they cover different forms of constructing the Amazon as a problem. Nonetheless, each Amazonian statement might be assigned to one or more codes. A statement can, for example, construct the Amazon as a problem of sovereignty and a problem of economic integration, or a problem of social development and conservation. Amazonian statements, thus, can be either coded as pure-types or mixed-types. Figure 1, below, portrays this operationalization strategy.

@@

Second, with the codebook in hand, each one of the authors, separately, hand-coded the same set of 1007 randomly selected Amazonian statements. This amount refers to 50% of all the Amazonian Statements identified. We chose to hand code half of the observations because there are several nuances in discourse in how presidents talk about the Amazon over time, and as a problem. As well, the size of the training set should increase with the number of categories (Grimmer, Roberts, and Stewart 2022). Since we have four categories, hand coding 50% of the statements mean we have a robust and reliable number of observations to be used for the training, and for validation, of the models. Automating the coding of half of the observations saved the authors over one month of work in comparison to manual coding. Once coded, the average intercoder agreement for hand-coded categories was 85%. For each non-matching coded observation, the authors discussed and sorted their disagreements, which were subsequently specified in the codebook.

Third, the hand-coded data is then randomly divided into a training set, containing 80% of the hand-coded observations (806 observations), and a validation set, containing the remaining 20% of the hand-coded data (201 observations). We chose to employ a support-vector machine (SVM) algorithm, a non-probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories, to label texts (Meyer et al. 2021; Noble 2006). As a robustness check, the SVM model is trained using the hand-coded training set and then employed to classify observations in the validation set. The trained SVM model was, on average, 82%, accurate in classifying observations in the validation set before being tuned. After the SVM model is tuned and the size of the training set is increased by including all hand coded observations, we use the model to automatically code the remaining 1007 Amazonian statements. The authors then randomly select 100 Amazonian statements automatically coded and find that the model is 97% accurate in coding these statements. The final dataset for analysis, excluding false positive matches, contains 1895 coded Amazonian statements (add a footnote for false positives here)).

@@

To analyze our data, we model the share of a specific pure problem-construction, versus all other problem-constructions, as the dependent variable, in relative to the settings in which a particular speech happens, as our independent variable. This means we predict the probability of a president constructing the Amazon as an issue of (1) environmental conservation, (2) economic integration, (3) social development, and (4) national sovereignty, separately, and in relation to the remaining problem-constructions (see table 1 below). We chose to focus on pure constructions to provide unambiguous interpretation and robust correlations. We divide setting in terms of non-Amazonian Brazilian states, Amazonian states within Brazil, Brasilia, Amazonian countries, and international. The level aggregation refers to geo-political settings that make sense in light of the Amazon, as a policy object. This aggregation combines different expectations presidents might have about transnational audiences in these settings. As well, Brasilia is a separate setting because of its’ unique location and since most presidential speeches are delivered in Brasilia. We control for yearly deforestation rates, inflation, election years, and peak years for Amazon appearing year in presidential speeches. Subsequently, we plot Amazonian statements and problem-constructions over time and by setting. We interpret the plots and model considering the literature alongside with multiple Amazon-related events and policies over the last 30 years.

@@

Third, employing lagged deforestation as a control variable has several constraints. We assume presidential discourse, policies, and outcomes are co-constitutive. Though, we lag annual deforestation one year since data for the year usually gets publicly released later and, frequently, there is a time difference to when discourses might refer to certain deforestation rates. We do think discourses capture general problem constructions that can be used to introduce, discuss, and justify policy and general outcomes. Throughout the analysis we carefully discuss how presidential discourses might relate to deforestation rates and outcomes by pointing to the patterns and correlations without making causality claims.

>>>>

To analyze how presidents construct the Amazon as a problem, we build upon Cezar’s 2020 dataset, which contains all official speeches by Brazilian Presidents from 1985 to 2019 scrapped from the archives of the Brazilian Presidential Library. We update the dataset by scraping and adding all official speeches from 2020 and 2021. The final dataset encompasses 6130 speeches. We, then, proceed to identify speeches that refer to the Amazon as a region, people, or forest. We do so by detecting all speeches in which the stem “amazon” appears. In Portuguese, the stem captures terms such as “Amazonia”, “Amazonica”, “Amazonidas”, “Amazonense(s)”, “Amazonas”, among others. We find that 946 speeches are, at least partially, about the Amazon.

Using the poldis R package (Sposito 2021), we extract two sentences before and after the sentence in which the stem “amazon” appears. We opt for picking two sentences around, rather than words, because sentences usually contain a cohesive idea. When two or more matches of the stem “amazon” appear in successive sentences, we get two sentences before the first match and two sentences after the last match. This is how our unit of analysis, Amazonian statements, are generated. Amazonian statements represent text portions that are meaningful for our specific purpose. This process yields 2014 unique Amazonian statements about the Amazon. On average, an Amazonian statement contains 123 words.

Our approach to coding Amazonian statements is threefold. First, we follow the Amazonian historiography literature to develop a codebook to identify Amazonian problem-constructions (see codebook in appendix). In their conceptualization, each problem-construction is mutually exclusive; that is, they cover different forms of constructing the Amazon as a problem. However, an Amazonian statement can be coded as referring multiple problem constructions. A statement can, for example, construct the Amazon as a problem of sovereignty and a problem of economic integration, or a problem of social development and conservation. Amazonian statements, thus, can be pure-type statements (i.e. constructs the Amazon as a single problem) or mixed-types (i.e. constructs the Amazon as multiple issues). Figure 1, below, portrays this operationalization strategy.

@@

Second, with the codebook in hand, each one of the authors separately hand-coded 1007 randomly selected Amazonian statements. This amount refers to 50% of all the Amazonian statements identified. We chose to hand code half of the observations because there are several nuances in how presidents talk about the Amazon over time, and as a problem. As well, the size of the training set should increase with the number of categories (Grimmer, Roberts, and Stewart 2022). Hand coding 50% of the statements mean we have a robust and reliable number of observations to be used for the training, and the validation, of the automated model. The average intercoder agreement for hand-coded categories was 85%. For each non-matching coded observation, the authors discussed and sorted their disagreements, which were subsequently specified in the codebook.

Third, the hand-coded data is randomly divided into a training set, containing 80% of the data (806 observations), and a validation set, containing the remaining 20% of the data (201 observations). We employ a support-vector machine (SVM) algorithm, a non-probabilistic linear classifier for binary categories, to label texts (Meyer et al. 2021; Noble 2006). To validate the model, the SVM algorithm is trained using the hand-coded training set and then employed to classify observations in the validation set. The trained SVM model was, on average, 82%, accurate in coding observations in the validation set. The SVM model is, then, tuned, re-trained using all the 1007 hand-coded observations, and used to automatically code the remaining 1007 Amazonian statements. As a final robustness check, the authors also randomly select 100 Amazonian statements automatically coded and find that the automated model is 97% accurate in coding these statements. The final dataset for analysis, excluding false positive matches, contains 1895 coded Amazonian statement ^[We also trained the model to identify false positive Amazonian statements. These are statements in which the stem “Amazon” is matched but the statements is not meaningful in relations to the policy object. For example, cases in which a president acknowledges the presence of the governor of the Amazon state, but is not really speaking about the Amazon.]. Automating the coding of half of the observations is estimated to have saved the authors over one month of work in comparison to manual coding.

@@

To analyze our data, we model the share of a specific pure problem-construction, as the dependent variable, relative to the settings in which a particular speech happens, as our independent variable. This means we predict the probability of a president constructing the Amazon as an issue of (1) environmental conservation, (2) economic integration, (3) social development, and (4) national sovereignty, separately, and in relation to the remaining problem-constructions (see table 1 below). We focus on pure problem constructions to provide unambiguous interpretation and more robust findings. We divide settings in terms of non-Amazonian Brazilian states, Amazonian states within Brazil, Brasilia, Amazonian countries, and international. The level aggregation refers to geo-political settings that make sense in light of the Amazon, as a policy object. This aggregation combines different expectations presidents might have about transnational audiences in these settings. Brasilia is separated as a setting due to its’ unique geolocation and since most presidential speeches are delivered in Brasilia. The model controls for yearly deforestation rates, inflation, election years, and peak years for Amazon in presidential speeches. The analysis also plots Amazonian statements and problem-constructions over time and by setting. We interpret the models and plots considering the literature, Amazon-related events, and policies over the last 40 years.

@@

Third, employing lagged deforestation as a control variable has several constraints. We assume presidential discourse, policies, and outcomes are co-constitutive. We lag annual deforestation one year since data for the year usually gets publicly released later and, frequently, there is a time difference to when discourses might refer to certain deforestation rates. We do think discourses capture general problem constructions that can be used to introduce, discuss, and justify policy and outcomes. Throughout the analysis we carefully discuss how presidential discourses might relate to deforestation rates and outcomes by pointing to the patterns and correlations, without making causality claims.
